---
title: "Package Tutorial"
author: "Cierra Disedare"
date: "2022-11-15"
output: html_document
---

# An Introduction to My R Package
### Class Project

My R package takes a portion of the data provided in a data set, cleans it in various ways, and works with it to create comprehensible and usable visualizations.

## Installation Instructions

First install the below packages to work with this data set, as it depends on them, and utilize the function codes without error.

```{r eval=FALSE, include=TRUE}
install.packages("tidyverse")
library("tidyverse")
```

```{r eval=FALSE, include=TRUE}
install.packages("ggplot")
library("ggplot")
```

```{r eval=FALSE, include=TRUE}
install.packages("ggplot2")
library("ggplot2")
```

```{r eval=FALSE, include=TRUE}
install.packages("parsnip")
library("parsnip")
```

```{r eval=FALSE, include=TRUE}
install.packages("readxl")
library("readxl")
disedare_data <- read_excel("Data/Molmol_database_20180716Dina.xlsx")
```

```{r eval=FALSE, include=TRUE}
install.packages("googlesheets4")
library("googlesheets4")
gs4_deauth()
# Upload data at the link. (https://docs.google.com/spreadsheets/d/1i-KjE51-tl0U9_PiqmTvVYSkh4UKXWCo/edit?usp=sharing&ouid=101255936712150037071&rtpof=true&sd=true).
#Once this is opened, download it to your local computer as an Excel Spreadsheet, and then upload it into your RStudio data folder. 
```

Function 1 of my package reads in the data set. This data set can be accessed at the link. [R_Data](https://docs.google.com/spreadsheets/d/1i-KjE51-tl0U9_PiqmTvVYSkh4UKXWCo/edit?usp=sharing&ouid=101255936712150037071&rtpof=true&sd=true). Once this is opened, download it to your local computer as an Excel Spreadsheet, and then upload it to your RStudio. 

This is the easiest way to access and utilize the data set. This is useful code for downloading, uploading, and then reading in excel data sets.

Below is function 1 of this package.
```{r eval=FALSE, include=TRUE}
library(readxl)
disedare_pkg1 <- function(file.path) {
  +     disedare_data <- read_excel("data/R_Data.xlsx")
  + }
```

To then view the action of this function run the code below.
```{r eval=FALSE, include=TRUE}
disedare_pkg1(disedare_data)
```

Function 2 of my package drops "NA" values from the data. This is useful code for altering the type of data in a column or row if it contains "NA" data, returning a cleaned data set.

Below is function 2 of this package.
```{r eval=FALSE, include=TRUE}
disedare_pkg2 <- function(file.path) {
            clean_data <- na.omit(disedare_data)
       return(clean_data)
}
```

To then view the action of this function run the code below.
```{r eval=FALSE, include=TRUE}
disedare_pkg2(disedare_data)
#or the code below
disedare_pkg2(clean_data)
```

Function 3 of my package selects four columns from the data set to work with. This code is useful for minimizing what data in the data set you are working with, and can be preparatory for running functions from the selected data. especially useful in larger data sets.

Below is function 3 of this package.
```{r eval=FALSE, include=TRUE}
library("tidyverse")
disedare_pkg3 <- function(file.path) {
  group_data <- disedare_data %>% 
    select(genus, species, mass_of_bat, building)
  return(group_data)
} 
```

To then view the action of this function run the code below.
```{r eval=FALSE, include=TRUE}
disedare_pkg3(disedare_data)
#or the code below
disedare_pkg3(group_data)
```

Function 4 of my package cleans up and alters a column of data, mass_of_bat, to make it user friendly and easy to work with. The mass_of_bat column is not reading in as numerics, despite being numbers. To alleviate that issue, I listed the column of mass_of_bat and altered it to become numerics.

```{r eval=FALSE, include=TRUE}
library("ggplot")
disedare_pkg4.1 <- function(file.path) {
  +     x <- list(disedare_data$mass_of_bat)
  +     return(x)
  + } 
disedare_pkg4.2 <- function(file.path) {
  +     x_num <- as.numeric(unlist(x))
  +     return(x_num)
  + } 
```

```{r eval=FALSE, include=TRUE}
disedare_pkg4.1(x)
disedare_pkg4.2(x_num)
```

Function 5 of my package creates a linear model regression of two columns from the data set, mass_of_bat and building, to determine if the location the bat is captured from has bearings on its growth or size. This code is response first, then predictor.

Below is function 5 of this package.
```{r eval=FALSE, include=TRUE}
library("parsnip")
disedare_pkg5 <- function(file_path) {
  model_fit <- lm(mass_of_bat ~ building, data = disedare_data)
  return(model_fit)
} 
summary(model_fit)
```

To then view the action of this function run the code below.
```{r eval=FALSE, include=TRUE}
disedare_pkg5(disedare_data)
# or use the code
disedare_pkg5(model_fit)
```

Those are all of the functions of this package.