---
title: "Package Tutorial"
author: "Cierra Disedare"
date: "2022-11-15"
output: html_document
---

# An Introduction to My R Package
### Subtitle

My R package is ..... and does.....
Words within *asterists* or _underscores_ gives italics.
Using **double** or __either__ gives bold.
When we go onto a new line does not create a new line on knitted file.

New paragraphs start after a line of space.

```{r}
sum(4, 6)
```

[1] 10

## Installation Instructions

```{r eval=FALSE, include=TRUE}
install.packages("phytools")
# IF YOU INCLUDE TEXT IN CODE CHUNK IT MUST BE COMMENTED  with #.
```
Go in and choose show nothing and don't run code off installation instructions.
Change include=FALSE to TRUE.

Can include text anywhere in document.

![Caption](path/to/image) #This allows you to include image, with a caption in the caption section, and then the path to the image (meaning the image has to be uploaded to Rstudio, cannot be JPEG). 

It is possible to include [hyper links](wright-lab.org).


